Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-19 paper.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct operation of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, telecommunications, internet of things and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, signal-processing pipelines and sophisticated software modules, in order to meet increasing computational power, flexibility demands, and adaptation to new scenarios and behaviors. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. Nonetheless, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, validating operation logic, ensuring correct behavior, providing compliance with the target system, incorporating knowledge about new problems and conditions, and supporting new software architectures and legacy designs (usually written in low-level languages). The present research discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct operation of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, telecommunications, internet of things, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, signal-processing pipelines and sophisticated software modules, in order to meet increasing computational power, flexibility demands, and adaptation to new scenarios and behaviors. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. Nonetheless, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, validating operation logic, ensuring correct behavior, providing compliance with the target system, incorporating knowledge about new problems and conditions, and supporting new software architectures and legacy designs. The present research discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}
